### 2016-02-07 paper.tex
R-2R DAC image
Updated caption of R2R dac figure
figure Successive Approx ADC

\begin{figure}
\includegraphics[width=6cm]{SA-ADC.png}
\centering
\caption{Block diagram of a 4-bit R-2R DAC\label{fig:r2r}}
\end{figure}

{\flushleft \em Analog to Digital Converters.}
An $n$-bit ADC converts an analog voltage (or current) to 
an equivalent $n$-bit digital data. The commonly used ADCs are
flash, successive-approximation, and sigma-delta ADCs. We give
a brief background on the successive-approximation ADC; the 
ADC we used for our expermients.

A successive-approximation ADC {\em SA-ADC} converts an analog
input to digital using a binary search technique.
In SA-ADC, a successive approximation register(SAR) containing 
a digital value is fed to an internal DAC and its output is 
compared to the input voltage. A sample and hold(SAH) circuit 
is used to supply constant input voltage to the comparator. 
A SA-ADC provides medium levels of accuracy and conversion time. 
The PUF output variation can occur because of microscopic variations 
in electrical components used in SAH circuit and internal DAC.
%It suffers from thermal noise for capacitors($kT/C$) which increases with temperature and is inversely proportional to the capacitance. However with higher capacitance, power consumption increases and accuracy decreases and usually a trade off is required.

>>>>

\begin{figure}
\includegraphics[width=9cm]{R-2R-DAC.png}
\centering
\caption{Block diagram of an n-bit R-2R DAC\label{fig:r2r}}
\end{figure}

{\flushleft \em Analog to Digital Converters.}
An $n$-bit ADC converts an analog voltage (or current) to 
an equivalent $n$-bit digital data. The commonly used ADCs are
flash, successive-approximation, and sigma-delta ADCs. We give
a brief background on the successive-approximation ADC; the 
ADC we used for our experiments.

A successive-approximation ADC {\em SA-ADC} converts an analog
input to digital using a binary search technique.
In SA-ADC, a successive approximation register(SAR) containing 
a digital value is fed to an internal DAC and its output is 
compared to the input voltage. A sample and hold(SAH) circuit 
is used to supply constant input voltage to the comparator. 
A SA-ADC provides medium levels of accuracy and conversion time. 
The PUF output variation can occur because of microscopic variations 
in electrical components used in SAH circuit and internal DAC.
\begin{figure}[h]
\includegraphics[width=6cm]{SA-ADC.png}
\centering
\caption{Block diagram of an n-bit successive-approximation ADC}
\end{figure}
%It suffers from thermal noise for capacitors($kT/C$) which increases with temperature and is inversely proportional to the capacitance. However with higher capacitance, power consumption increases and accuracy decreases and usually a trade off is required.
